### 2023-02-18 paper.tex
first ideas for offline concepts

        programming enviroments for text based programming:
            \begin{itemize}
                \item KUKA 
                \item ABB RobotStudio
                \item Fanuc RobotStudio
                \item Staubli TX
                \item Adept
                \item Motoman
            \end{itemize}
        (b1 p. 113)

@@

>>>>

        commands mostly define movements from on point to another and how to interpolate between them %source?

        programming enviroments for text based from the most common robot manufacturers %quote this?

        examples 
        abb robot studio
        uses rapid language %source?

        kuka officelite
        uses krl language %source?

        in addition to the textual programming features most of the enviroments also offer a graphical programming interface

        the main concepts used in these enviroments are controlling the robot by moving its arms on different axis and rotating it on those or to simulate a controller (representation of the ones used in the online concepts)

        kuka mainly uses the second concept where as abb uses both

        (https://new.abb.com/products/robotics/robotstudio)

        some enviroments even make use of ar technologie to show the roboter and its movements in the real world 
            \end{itemize}

        example robot studio

@@

        uses a 3d scenery viewer which shows the simulated production enviroment

        can simulate multiple robots and multiple tasks apart from robot movements

        example visual components

        (https://new.abb.com/products/robotics/robotstudio)
